---
title: "R Notebook"
output: html_notebook
---

Re-run extract extracting region data.


```{r setup}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
knitr::opts_chunk$set(cache=TRUE)
```

# Choose what parts to rerun
Choose parts to run adn number of iterations.

```{r choose_parts_run}
extract_stata_files <- FALSE
clean_and_merge <- TRUE
run_imputation <- TRUE
aggregate_data <- TRUE
num_iters <- 20000
```


# Functions and foldernames

```{r read_data}
library (foreign)

## Only runs if set convert.factors to FALSE, files otherwise too big 

## Functions
# read and select vars function for a specific file
ReadAndSelect <- function (x, myvars ){
  a <- read.dta(paste("../Data_unzipped/Data_SSEASI/", x, sep = "/"), convert.factors = FALSE, convert.dates = FALSE)
  a <- a [ , names(a) %in% myvars]
  a$ctr.type.2digit <- paste (substr(x,1,2), substr(x, 5,6), sep = "_")
#  a$missing.vars <- paste (setdiff(myvars, names(a)), collapse = ", ")
#  a [,setdiff(myvars, names(a))] <- NA
#  Convert factors to character vectors
#  identifyfactors <- sapply(a, class) == "factor"
#  a [, identifyfactors] <- lapply (a [, identifyfactors], as.character)
  a
}

# Read all files and save in a list
ReadAllFiles <- function (filetype, varlist){
  filenames <- substr(filetype, 1, 8)
  listdata <- list()
  listvars <- list()
  for (i in 1:length (filetype)){
    assign(filenames[i], ReadAndSelect (filetype[i], varlist))
    listdata[[i]] <- get(filenames[i])
    # save (list = filenames[i], file = paste (write, filenames[i], ".Rdata", sep = ""))
    listvars[[i]] <- varlist %in% names(get(filenames[i]))
    names(listvars[[i]]) <- varlist
    rm (list = filenames[i])
  }
  names(listdata) <- filetype
  names(listvars) <- filetype
  list (listvars, listdata)
}

folder <- "india"
names(folder) <- "india"

```

# REad files
```{r read_files}
if (extract_stata_files == TRUE){
  # list files in folder for India
  # "../Data_unzipped/Data_SSEASI/"
  allfiles <- tolower(list.files("../Data_unzipped/Data_SSEASI/", pattern = "^IA"))
  
  # select only .dta files
  allfiles <- allfiles [substr(allfiles, 10,12) == "dta"]
  
  table(stringr::str_sub(allfiles, 3,4))
  ## Women variables want
  # select all KR datasets for all DHS
  irvars <- c("ctr.type.2digit", "v001", # My and DHS country code
              "v000", "v002", "v003", # cluster number, household number, respondent line number
              "v763a", "v857") # STD data
  
  ir <- allfiles [substr(allfiles, 3,4) == "ir"]
  ir.files <- ReadAllFiles(ir, irvars)
  save(ir.files, file = paste0(names(folder), "/irfiles.Rdata"))  
  rm(ir.files)
  
  ## "kid" recode variables want
  krvars <- c("ctr.type.2digit","v001", # my country and type, DHS country code
              "v000", "v002", "v003", # cluster number, household number, respondent line number
              "bidx", # Birth index
              "v005", # sample weight
              "v006", "v007", "v008", # month and year of interview and century month
              "b3", # century month for date of birth of child
              "m19", # weight of child at birth (m18 subjective)
              "h3", # "h3d", "h3m", "h3y", # immunisation
              "h5", # "h5d", "h5m", "h5y", # immunisation
              "h7", # "h7d", "h7m", "h7y", # immunisation
              "h9", # "h9d", "h9m", "h9y", # immunisation
              "v404", "m39", # breastfeeding,
              "hw8", # weight/age standard deviation (original, found in earlier DHS)
              "hw71") # Weight/Age standard deviation (new WHO) 
  
  # Identify data files # select all KR datasets for all DHS
  kr <- allfiles [substr(allfiles, 3,4) == "kr"]
  
  # Read in all KR6 data files and label according to first 8 characters of name - as per DHS coding, select variables want t keep
  # and save in .Rdata format
  kr.files <- ReadAllFiles(kr, krvars)
  save(kr.files, file = paste0(names(folder), "/krfiles.Rdata"))  
  rm(kr.files)
  
  ## Household data
  hrvars <- c("ctr.type.2digit", # my country and type
              "hv000", "hv001", "hv002",  # country code, cluster code, household number
              "hv024", # State code
              "hv006", # Month of interview
              "hv007", # Year of interview 51 4 N I 1 0 No No
              "hv008", # Date of interview (CMC)
              "hv009", "hv216",  # Overcrowding
              "hv226", "hv242", "hv241") # indoor air pollution
  
  hr <- allfiles [substr(allfiles, 3,4) == "hr"]
  hr.files <- ReadAllFiles (hr, hrvars)
  save(hr.files, file = paste(names(folder), "hrfiles.Rdata", sep = "/"))  
  rm(hr.files)
  
  ## HIV data
  hiv5 <- haven::read_dta("//cfsg01.campus.gla.ac.uk/SSD_Dept_Data_D/HAW/HAWPublic/PublicHealth/DMSBiolinnc/DHS/iaar51fl.dta")
  hiv7 <- haven::read_dta("//cfsg01.campus.gla.ac.uk/SSD_Dept_Data_D/HAW/HAWPublic/PublicHealth/DMSBiolinnc/DHS/iaar71fl.dta")
  
  arvars <- c("hivclust","hivnumb", "hivline", # link variables
              "hiv03") # hiv status
  
  hiv5 <- hiv5[ , arvars]
  hiv7 <- hiv7[ , arvars]
  hiv5$dhs <- 5
  hiv7$dhs <- 7
  
  ar.files <- rbind(hiv5, hiv7)
  rm(hiv5, hiv7)
  
  save(ar.files, file = "//cfsg01.campus.gla.ac.uk/SSD_Dept_Data_D/HAW/HAWPublic/PublicHealth/DMSBiolinnc/DHS/arfiles.Rdata")  
}
```

# Combine files
```{r combine_files}
if(clean_and_merge  == TRUE){
      
    list.files("india")
    library (plyr)
    folder <- "india"
    names(folder) <- "india"
    ## HIV change to TRUE and FALSE
    ## For DHS 5 and 6 use maternal HIV, use STD for earlier versions as proxy for HIV
    load(file = "//cfsg01.campus.gla.ac.uk/SSD_Dept_Data_D/HAW/HAWPublic/PublicHealth/DMSBiolinnc/DHS/arfiles.Rdata")
    ar.data <- ar.files
    rm(ar.files)
    # three unique values only and no missings. only 3 samples with indeterminate so drop
    ar.data <- ar.data[!ar.data$hiv03 == 7,]
    ar.data$hiv <- ar.data$hiv03
    ar.data$hiv03 <- NULL
    
    load(file = paste(names(folder), "irfiles.Rdata", sep = "/"))
    ir.data <- do.call(rbind.fill, ir.files[[2]])
    rm(ir.files)
    ir.data <- ir.data [!duplicated(paste(ir.data$ctr.type.2digit, ir.data$v001, ir.data$v002, ir.data$v003, sep = "_")), ]
    
    # STD variable changes so use either, if either is completely missing assign it to NA
    if (is.null(ir.data$v857)) ir.data$v857 <- NA
    if (is.null(ir.data$v763a)) ir.data$v763a <- NA
    
    ir.data [ , c("v763a", "v857")] <- lapply (ir.data [ , c("v763a", "v857")], function (x) ifelse(is.na(x), 99, x))
    ir.data$hiv_proxy <- NA
    ir.data$hiv_proxy [ ir.data$v763a ==0 | ir.data$v857 == 0] <- 0
    ir.data$hiv_proxy [ ir.data$v763a ==1 | ir.data$v857 == 1] <- 1
    ir.data <- ir.data [ , !names(ir.data) %in% c("v763a", "v857") ]
    ir.data$dhs <- stringr::str_sub(ir.data$ctr.type.2digit, 4,4)
    ir.data$v763a <- NULL
    ir.data$v857 <- NULL
    
    ir.data <- merge(ir.data, ar.data, by.x = c("dhs","v001", "v002", "v003"),
                        by.y = c("dhs","hivclust", "hivnumb", "hivline"),
                        all.x = TRUE)
    
    ## Kid file
    load(file = paste(names(folder), "krfiles.Rdata", sep = "/"))
    kr.data <- do.call(rbind.fill, kr.files[[2]])
    kr.data <- kr.data [!duplicated(paste(kr.data$ctr.type.2digit, kr.data$v001, kr.data$v002, kr.data$v003, kr.data$bidx, sep = "_")), ]
    rm(kr.files)
    
    ## Merge maternal HIV onto kid file
    kr.data <- merge(kr.data, ir.data, by = c("ctr.type.2digit", "v000", "v001", "v002", "v003"),
                        all.x = TRUE)
    rm(ir.data)
    
    # 1000*mean(kr.data$hiv, na.rm = TRUE)
    # 1000*mean(kr.data$hiv_proxy, na.rm = TRUE)
    
    # 2. lbw - DHS 2 to 6
    kr.data$lbw <- kr.data$m19 <= 2500
    kr.data$lbw[kr.data$m19 >= 9000] <- NA
    
    # age in months
    kr.data$age.in.months <- kr.data$v008 - kr.data$b3 # century month survey - century month child's age
    
    # 3. incomplete immunisation - DHS 1-6
    # recode vaccination variable
    # 0 No
    # 1 Vaccination date on card
    # 2 Reported by mother
    # 3 Vaccination marked on card
    # 8 Don't know
    # (m) 9 Missing
    kr.data [, c("dtp1", "dtp2", "dtp3", "measles")] <- 
      lapply(kr.data [ , c("h3", "h5", "h7", "h9")], 
             function (x) ifelse (x==9, NA, x %in% 1:3 ))#
    kr.data$vac <- "complete" #  
    kr.data$vac [ kr.data$age.in.months > (2+1) & kr.data$h3 == FALSE ] <- "incomplete"
    kr.data$vac [ kr.data$age.in.months > (3+1) & kr.data$h5 == FALSE ] <- "incomplete"
    kr.data$vac [ kr.data$age.in.months > (5+1) & kr.data$h7 == FALSE ] <- "incomplete"
    kr.data$vac [ kr.data$age.in.months > (12+1) & kr.data$h9 == FALSE ] <- "incomplete"
    kr.data$vac [ is.na(kr.data$dtp1) & is.na(kr.data$dtp2) & is.na(kr.data$dtp3) &
                     is.na(kr.data$measles)] <- NA # set to missing if all data missing
    kr.data$inc.imm <- ifelse(kr.data$vac == "incomplete", TRUE, FALSE)
    
    # 4 non-exclusive breastfeeding - Same coding from DHS 1 to DHS 6, M39 correct code
    kr.data$ebf <- kr.data$v404
    kr.data$ebf [ !is.na(kr.data$ebf) & kr.data$m39 !=0 ] <- 0  # any food other than breastmilk
    kr.data$non.ebf <- ifelse(kr.data$ebf == 1, FALSE, TRUE)
    kr.data$non.ebf [ kr.data$age.in.months >6 ] <- NA # set to NA if aged more than 6 months
    # Later on will impute this
    
    ## DHS 1-4 for longitudinal use HW8 otherwise use HW71
    # 5. Malnutrition HW71 Weight/Age standard deviation (new WHO) 98 4 N I 1 0 No No
    # -600:500 9996 Height out of plausible limits 9997 Age in days out of plausible
    # limits 9998 Flagged cases (m) 9999 Missing (na) Not applicable 
    # http://www.who.int/bulletin/volumes/85/6/06-034421/en/ In our final sample for
    # each DHS survey, we excluded children without data on height, weight, age or
    # sex. We used the new cut-offs recommended by the WHO for data exclusion.5
    # Thus, data were excluded if a child’s HAZ was below –6 or above +6, WAZ (eight for age SD)was
    # below –6 or above +5, WHZ was below –5 or above +5, or BMIZ was below –5 or
    # above +5, because these extreme values were most likely a result of errors in
    # measurement or data entry.5
    ## therefore hw71 has been multiplied by 100 to avoid decimal points in data storage
    
    kr.data$maln <- kr.data$hw71
    kr.data$maln [ kr.data$maln >500 ] <- NA # set missing values
    kr.data$maln <- ifelse (kr.data$maln < -200, TRUE, FALSE)
    
    kr.data$maln.long <- kr.data$hw8
    kr.data$maln.long [ kr.data$maln.long >500 ] <- NA # set missing values
    kr.data$maln.long <- ifelse (kr.data$maln.long < -200, TRUE, FALSE)
    
    kr.data <- kr.data [ , ! names(kr.data) %in% c("b3", "dtp1", "dtp2", "dtp3", "measles","h3", "h5", "h7", "h9", "vac","v404", "m39", "ebf")] 
    save (kr.data, file = paste (names(folder), "kr_processed.Rdata", sep = "/"))
    
    ##Household variables
    load(file = paste(names(folder), "hrfiles.Rdata", sep = "/"))
    hr.data <- do.call(rbind.fill, hr.files[[2]])
    hr.data <- unique(hr.data)
    rm(hr.files)
    
    # 5 indoor air pollution - DHS 5 and 6 have all vars, DHS 4 has fuel type but not cooking location. DHS 1-3 has nil
    # DHS 4 recode map
    #* indicates potentially polluting
    # HV226 46 2 0 N S Type of cooking fuel
    # values: value label
    # 1 Electricity
    # 2 LPG, natural gas
    # 3 Biogas
    # 4 Kerosene *
    # 5 Coal, lignite
    # 6 Charcoal
    # 7 Firewood, straw *
    # 8 Dung *
    # 96 Other
    # 99 Missing value
    # ranges: lower upper
    # 1 8
    # 96 96
    ## DHS 5 and coding
    # HV226 Type of cooking fuel 
    # 1 Electricity
    # 2 LPG
    # 3 Natural gas
    # 4 Biogas
    # 5 Kerosene *
    # 6 Coal, lignite
    # 7 Charcoal
    # 8 Wood *
    # 9 Straw/shrubs/grass *
    # 10 Agricultural crop *
    # 11 Animal dung *
    # 95 No food cooked in house
    # 96 Other
    # (m) 99 Missing
    ## For longitudinal analysis including 4, 5 and 6 use indoor.air
    hr.data$survey.type <- substr(hr.data$hv000,3,3)
    hr.data$indoor.air <- (hr.data$hv226 %in% c(4,7,8) & hr.data$survey.type == 4) | 
                          (hr.data$hv226 %in% c(5, 8, 9, 10, 11) & hr.data$survey.type %in% 5:6)
    hr.data$indoor.air [(hr.data$hv226 == 99 & !is.na(hr.data$hv226)) | hr.data$survey.type %in% 1:3] <- NA
    hr.data$indoor.air <- hr.data$indoor.air
    
    # HV242 Household has separate room used as kitchen 
    # 0 No
    # 1 Yes
    # (m) 9 Missing
    
    ## For single time analysis use the  one which takes into account cooking location
    # HV241 Food cooked in the house/ separate building
    # 1 In the house
    # 2 In a separate building
    # 3 Outdoors
    # 6 Other
    # (m) 9 Missing
    # (na) Not applicable
    hr.data$indoor.air  [hr.data$hv242 %in% c(2,3,6) & !is.na(hr.data$hv242)] <- FALSE
    
    ## 6 Overcrowding - as per discussion >5 persons per household, more cople version commented out
    # HV009 Number of household members 
    # 0:90
    # HV216 Number of rooms used for sleeping
    # 0:24
    # (m) 99 Missing
    # hr.data$hv216 [ hr.data$hv216 == 99] <- NA
    # hr.data$overcrowd <- (hr.data$hv009 / hr.data$hv216 ) > 3
    hr.data$overcrowd <- hr.data$hv009  > 5
    
    ### 7 State
    # head(hr.data$hv024)
    hr.data <- hr.data [ , c("ctr.type.2digit" ,"hv000", "hv001", "hv002", "hv008", "hv024","indoor.air", "indoor.air", "overcrowd")]
    
    
    save (hr.data, file = paste (names(folder), "hr_processed.Rdata", sep = "/"))
    
    final <- merge (kr.data, hr.data, 
                    by.x = c("ctr.type.2digit", "v001", "v002"), # country, cluster, household, cent month
                    by.y = c("ctr.type.2digit", "hv001", "hv002"),
                    all.x = TRUE)
    final <- final [ !duplicated(paste(final$ctr.type.2digit, final$v001, final$v002, final$v003, final$bidx, sep = "_")), ]
    rm(hr.data, kr.data)
    
    ## We do not want age stratified analysis, only to exclude children aged over 4
    ## (as per email from Harish July 2015) Want to assume that the proportion of
    ## children aged 6 to 48 months who had non-EBF is the same as those who are
    ## currently non-EBF within the other strata - so set variable to 2 if aged 6 months to 4 years
    # apply the proportion wihtin the aggregation analysis
    # at this stage set the non-ebf in children aged over 6 months to FALSE
    
    final$age <- 0
    final$age [ final$age.in.months <= 6] <- 1
    
    final$age [  final$age.in.months >6 & final$age.in.months <= (4*12)] <- 2
    final$non.ebf [ final$age == 2] <- FALSE
    
    ## Set non-ebf to NA, as will be imputing this later, assumes non-EBF same in other age groups
    final$non.ebf [final$age != 1] <- NA
      
    
                        # country, state, century month, age, weight, 
    final <- final [ , c("ctr.type.2digit", "hv024","v008", "age", "v005", 
                         "lbw", "hiv", "hiv_proxy", "inc.imm", "non.ebf", "maln", "maln.long", "indoor.air", "overcrowd")]
    save (final, file = paste (names(folder), "final.Rdata", sep = "/"))
}
```
# Impute missing variables
Run multiple imputation with only one sample. Do a sensitivity anlaysis later with another imputed sample

```{r impute}
if(run_imputation == TRUE){
  library(mice)
  final_imp <- final[ , c("age", "lbw", "hiv", "hiv_proxy", "inc.imm", "non.ebf", "maln", "maln.long", "indoor.air", "overcrowd")]
  final_imp$age <- final_imp$age - 1
  final_imp[] <- lapply(final_imp, function(x) factor(as.numeric(x)))
  
  final_imp_done <- mice(final_imp, m = 1, method = "logreg")
  saveRDS(final_imp_done, file = paste (names(folder), "final_imputed.Rdata", sep = "/"))
  
  final_imp_done <- readRDS(file = paste (names(folder), "final_imputed.Rdata", sep = "/"))
  load(file = paste (names(folder), "final.Rdata", sep = "/"))
  final_imp <- mice::complete(final_imp_done)
  setdiff(names(final), names(final_imp))
  
  final_imp <- cbind(final[, c("ctr.type.2digit", "hv024", "v008", "v005", "age")],
                     final_imp [ ,c("lbw", "hiv", "inc.imm", "non.ebf", 
                                    "maln.long", "indoor.air", "overcrowd")])
  saveRDS(final_imp, file = paste (names(folder), "final_imputed_merged.Rdata", sep = "/"))
}

```


# Aggregate data

```{r aggregate}
if(aggregate_data == TRUE) {
  final <- readRDS(file = paste (names(folder), "final_imputed_merged.Rdata", sep = "/"))
  final$n <- 1
    
    # Load data table for fast aggregation
  library (data.table)
  final <- data.table (final)
  final.agg <- final[, list(n=sum(as.numeric(n)), weight = sum(as.numeric(v005)), year =
                              mean(as.numeric(v008))), by=list(ctr.type.2digit, hv024, age,
                                                               lbw, hiv, inc.imm, 
                                                               non.ebf, indoor.air, 
                                                               overcrowd, maln.long)] 
  
  final.agg <- as.data.frame (final.agg)
  final.agg$year <- 1900 + (final.agg$year -1)/12 
  
  # Convert all factors to numeric 01
  final.agg[,c("lbw", "hiv", "inc.imm", "non.ebf", 
                       "indoor.air", "overcrowd", "maln.long")] <- 
    lapply(final.agg[,c("lbw", "hiv", "inc.imm", "non.ebf", 
                        "indoor.air", "overcrowd", "maln.long")],
                                    function(x) as.integer(as.character(x)))
  
  save (final.agg, file = paste (names(folder), "region aggregated data.Rdata", sep = "/"))
  write.csv (final.agg, file = paste (names(folder), "region aggregated data.csv", sep = "/"), row.names = FALSE)
}
```

# Calculate dirichlet 
```{r dirlecht}
library(MCMCpack)
library(tidyverse)
library(stringr)
load("india/region aggregated data.Rdata")

## Create survey variable
final.agg <- final.agg %>% 
  mutate(survey = str_sub(ctr.type.2digit, 4,5))

## Add copy of dataset with all states together 
# define whole of india as hv024 = 0
all_india <- final.agg %>% 
  group_by(ctr.type.2digit, survey,
           age, lbw, hiv, inc.imm, non.ebf, indoor.air, overcrowd, maln.long) %>% 
  summarise(n = sum(n), weight = sum(weight), year = mean(year)) %>% 
  ungroup() %>% 
  mutate(hv024 = 0)

final.agg <- bind_rows(all_india, final.agg) %>%
  mutate(survey_state = paste(survey, hv024, sep = "_"))

surveys_states <- unique(final.agg$survey_state) %>%  sort()
names(surveys_states) <- surveys_states

## Combine and rewight Telangana (36) and Andra Pradesh(2) in 2015 (DHS 72)
ap_tl <- final.agg %>% 
  filter(survey_state %in% c("72_36", "72_2"), hv024 %in% c(2, 36)) %>% 
  group_by(ctr.type.2digit, age, lbw, hiv, inc.imm, non.ebf, indoor.air, overcrowd, maln.long, survey) %>% 
  summarise(n = sum(n), weight = sum(weight), year = mean(year)) %>% 
  ungroup() %>% 
  mutate(hv024 = 2, survey_state = "72_2")

final.agg <- final.agg %>% 
  filter(!(survey_state %in% c("72_36", "72_2") & hv024 %in% c(2, 36))) %>% 
  bind_rows(ap_tl) %>% 
  arrange(ctr.type.2digit, survey, hv024)

## Reweight percentage to state by normalising the weights
final.agg <- final.agg %>% 
  group_by(ctr.type.2digit, hv024, survey, survey_state) %>% 
  mutate(weight_norm = weight/sum(weight)) %>% 
  ungroup()

SampleStates <- function (chosen_survey, chosen_state, 
                           chosen_rfs = c("lbw", "inc.imm", "non.ebf", "maln.long",
                                          "overcrowd", "indoor.air", "hiv"),
                           chosen_ages = 1:2,
                          n_iter = num_iters){ # 
  ## Samples from Dirlecht distribution for selected risk factors
  ## Uses prior of 1 for all parameters (ie a uniform prior)

    ## Create dataset of complete combinations
  if(length(chosen_rfs) == 7)  state_complete <- expand.grid(0:1, 0:1, 0:1, 0:1, 0:1, 0:1, 0:1)
  if(length(chosen_rfs) == 6)  state_complete <- expand.grid(0:1, 0:1, 0:1, 0:1, 0:1, 0:1)
  if(length(chosen_rfs) == 5)  state_complete <- expand.grid(0:1, 0:1, 0:1, 0:1, 0:1)
  names(state_complete) <- chosen_rfs

  # Select relevant survey and state
  selected_survey_state <- final.agg %>% 
    filter(survey == chosen_survey, hv024 == chosen_state)
  
  ## Aggregate further as per ages, intially both age groups
  dots <- sapply(chosen_rfs, . %>% {as.formula(paste0('~', .))})
  state_count <- selected_survey_state %>% 
    select(age, lbw, inc.imm, non.ebf, inc.imm, maln.long, indoor.air, overcrowd, hiv, n, weight_norm) %>% 
    mutate_at(vars(-weight_norm), as.integer) %>% 
    filter(age %in% chosen_ages) %>% 
    group_by_(.dots = dots) %>% 
    summarise(n = sum(n),
              weight_norm = sum(weight_norm))
  ## Combine with complete list of risk factors for n's and weights
  state_count <- state_complete %>% 
    left_join(state_count, by = chosen_rfs) %>% 
    mutate(n = if_else(is.na(n), 0L, n),
           weight_norm = if_else(is.na(weight_norm), 0, weight_norm))

  ## Obtain samples with a prior of 1/128, ie assume same proportion in each category
  smpls <- rdirichlet(n_iter, state_count$n + 1/128)
  # Recalcualte proportions based on weights
  # Shape weights into same format as Dirichlet
  wt_mtrx <- t(state_count$weight_norm)
  wt_mtrx <- wt_mtrx[rep(1,nrow(smpls)), ]
  # Multiple weights and normalise so same proportions
  smpls_new <- smpls * wt_mtrx
  smpls_new <- smpls_new /rowSums(smpls_new)
  ## Output samples and varlist
  list(smpls = smpls_new, state_complete = state_complete)
}
# Select earliest and latest DHS surveys to include in analysis
code_earliest <- 42
code_latest <- 72

## Estimate for DHS latest
states_dhs_latest <- unique(final.agg$hv024[final.agg$survey == code_latest]) %>%  sort()
names(states_dhs_latest) <- states_dhs_latest

res_states_dhs_latest <- map(states_dhs_latest, ~ 
                         SampleStates(chosen_survey = code_latest, chosen_state = .x,
                                      chosen_rfs = c("lbw", "inc.imm", "non.ebf", "maln.long",
                                          "overcrowd", "indoor.air", "hiv")))
## Estimate for DHS 4
states_dhs_earliest <- unique(final.agg$hv024[final.agg$survey == code_earliest]) %>%  sort()
names(states_dhs_earliest) <- states_dhs_earliest

res_states_dhs_earliest <- map(states_dhs_earliest, ~ 
                         SampleStates(chosen_survey = code_earliest, chosen_state = .x,
                                      chosen_rfs = c("lbw", "inc.imm", "non.ebf", "maln.long",
                                          "overcrowd", "indoor.air", "hiv")))
```

# Transpose lists and extract
```{r list_transpose}
state_complete <- res_states_dhs_earliest$`0`[[2]]
res_states_dhs_earliest <- transpose(res_states_dhs_earliest)
res_states_dhs_earliest <- res_states_dhs_earliest[[1]]

res_states_dhs_latest <- transpose(res_states_dhs_latest)
res_states_dhs_latest <- res_states_dhs_latest[[1]]
```



# Convert HV
FROM UNAIDS
2000|53403|119369000
2006|65678|118170000
2013|46087|116176000

Multiply HIV cases from UNAIDS by cases from all of india to get odds ratio, then apply to each row.

```{r impute_hiv}
# Calculate India HIV odds from data
CalculateOddsIndia <- function (x) sum(x$hiv * x$n) / sum((1-x$hiv) * x$n)

CalculateOddsIndia(final.agg %>%  filter(survey == code_earliest))

# Calculate odds ratio for UNAIDS versus DHS (approximate) odds
OR_latest   <- 46087/(116176000-46087) / CalculateOddsIndia(final.agg %>%  filter(survey == code_latest))
OR_earliest <- 53403/(119369000-53403) / CalculateOddsIndia(final.agg %>%  filter(survey == code_earliest))

# Correct proportion HIVs based on UNAIDS to imputed odds ratio 
# Cdds raito for all of India HIV to UNAIDS HIV
# Applies this to reduce proportion with HIV


LogOdds <- function(x) log(x/(1+x))
Prob <- function(x) exp( x/(1-x) )
  
CorrectHIV <- function(x, OR) {
  ## Convert proportion to log-odds
  x[] <- qlogis(x)
  ## Calculate new log-odds of being in HIV group
  x[,65:128] <- x[,65:128] + log(OR)
  ## Calculate new odds of being in non HIV group
  x[,1:64]   <- x[,1:64]   - log(OR)
  ## Convert odds back to proportion
  x[] <- plogis(x)
  ## Return result
  x
}

# Note `0` is all of India
100*sum(res_states_dhs_earliest$`0`[, 65:128]) /  sum(res_states_dhs_earliest$`0`[,])
100*sum(res_states_dhs_latest$`0`[, 65:128]) /  sum(res_states_dhs_latest$`0`[,])

# Impute HIV for dhs_earliest
res_states_dhs_earliest <- map(res_states_dhs_earliest, CorrectHIV, OR = OR_earliest)
res_states_dhs_latest <- map(res_states_dhs_latest, CorrectHIV, OR = OR_latest)

100*sum(res_states_dhs_earliest$`0`[, 65:128]) /  sum(res_states_dhs_earliest$`0`[,])
100*sum(res_states_dhs_latest$`0`[, 65:128]) /  sum(res_states_dhs_latest$`0`[,])

```


# Save dirlechts
```{r save_dirlechts}
saveRDS(res_states_dhs_earliest, file = "India/dirlecht_dhs_earliest.Rds")
saveRDS(res_states_dhs_latest, file = "India/dirlecht_dhs_latest.Rds")
saveRDS(state_complete, file = "India/dirlecht_risk_factor_order.Rds")

```



